---
# Documentation: https://sourcethemes.com/academic/docs/managing-content/

title: "Courses Completed"
subtitle: ""
summary: ""
authors: []
tags: []
categories: []
date: 2020-07-03T18:50:01-04:00
lastmod: 2020-07-03T18:50:01-04:00
featured: false
draft: false
share: false
---
<style>
summary h3{ 
  display: inline-block;
  font-size:20px;
  font-family:"Quicksand";
  color: #e3e0bc !important;
}
h1{
  color: #476e52 !important;
}
summary{
  height: 30% !important;
}
</style>
```{r setup,include=FALSE}
library(tidyverse)
library(DT)
library(widgetframe)
```
```{r table,echo=FALSE}
path<-"../../static/files/"
first_name<-"first_year.csv"
second_name<-"second_year.csv"

first_year<-read.csv(paste(path,first_name,sep=""))
second_year<-read.csv(paste(path,second_name,sep=""))


df<-rbind(second_year,first_year) %>% datatable(rownames = FALSE,
          options = list(
            pageLength = 5,
            autoWidth = TRUE,
            columnDefs = list(list(
              className = 'dt-left',
              targets = 0),
              list(className = 'dt-center', targets = 1))))
```
---

<details>
<summary>
<h3>University of Toronto</h3>
</summary><p>
```{r output, echo=FALSE}
widgetframe::frameWidget(df, height=320)
```
</p></details>

<details>
<summary>
<h3>EdX (online)</h3>
</summary>
<p>
- [x] HarvardX Data Science: <span style="padding-left: 5px; display:inline">*R Basics*</span>

- [x] HarvardX Data Science: <span style="padding-left: 5px; display:inline">*Visualization*</span>

- [x] HarvardX Data Science: <span style="padding-left: 5px; display:inline">*Probability*</span>

- [x] HarvardX Data Science: <span style="padding-left: 5px; display:inline">*Inference and Modeling*</span>

- [x] HarvardX Data Science: <span style="padding-left: 5px; display:inline">*Productivity Tools*</span>

</p>
</details>


<details>
<summary>
<h3>Kaggle Micro-courses (online)</h3>
</summary>
<p>
- [x] Intro to Machine Learning
- [x] Intermediate Machine Learning
- [x] Feature Engineering
- [x] Deep Learning

</p>
</details>