---
title: Distributions
author: ''
date: '2020-07-12'
slug: variety
categories:
  - R
tags:
  - Statistics and Probability
subtitle: ''
summary: 'Curious to see if your data follows a particular distribution?'
authors: []
lastmod: '2020-07-12T16:09:53-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
draft: TRUE
---
<style>
.bod{
  font-family: Arial;
  font-size: 10pt;
  display: inline-block;
  margin-left: 15px;
  text-indent: 50px;
}
h2{
  text-decoration: underline;
  padding-top: 15px;
  font-family: "Arial";
  text-align: left;
}
<!-- h3{  -->
<!--   display: list-item; -->
<!--   list-style-type: upper-roman;; -->
<!--   list-style-position: inside; -->
<!--   font-size:17px; -->
<!--   font-family:"Cambria"; -->
<!--   font-style: italic; -->
<!--   margin-left: 7px; -->
<!-- } -->

</style>

## Normal Distribution

<p class="bod">
Probably one of the most important distributions in statistics, the normal distribution is most notably used in hypothesis testing and confidence intervals.
</p>

### Testing out the Central Limit Theorem

<p class="bod">
To make an illustrative point, RStudio's built-in dataset BJsales will be used. The data describes the number of sales every day for some consecutive months. Its probability density was graphed below.
</p>

```{r prelim, echo=FALSE, include=FALSE, eval=TRUE}
library(tidyverse)
library(ggplot2)
library(gridExtra)

data(BJsales)
numeric_data <- as.numeric(BJsales)
X <- mean(numeric_data)
B <- 10000

sample_means <- replicate(length(numeric_data), {
  samples <- sample(numeric_data, 30, replace=TRUE)
  mean(samples)
})

df <- data.frame(numeric_data, sample_means)

plot_dist <- df %>% 
  ggplot(aes(x=numeric_data)) +
  geom_density(fill="gray") +
  ggtitle(NULL) +
  xlab("BJ Sales") +
  ylab("Probability Density") +
  ylim(c(0, 0.09)) +
  theme_classic() +
  theme(axis.title.y = element_text(size = rel(0.9), angle = 90))

plot_sample <- df %>% 
  ggplot(aes(x=sample_means)) +
  geom_density(fill="gray") +
  ggtitle(NULL) +
  xlab("Sample Means") +
  ylab("Probability Density") +
  theme_classic() +
  theme(axis.title.y = element_text(size = rel(0.9), angle = 90))
```

```{r plot, fig.show='hold', echo=FALSE, fig.dim=c(3.2,2.5)}
plot_dist
```

<p class="bod">
Notice how the distribution is bimodal with one peak centered at 217 and the other at 257! Now look what happens when you take 30 samples from  
</p>

<br>

```{r plot2, fig.show='hold', echo=FALSE, fig.dim=c(3.2,2.5)}
plot_sample
```









